### 2019-06-30 ThesisJo/2_publications.tex
2019-06-29

We present four journal published papers concerned with \emph{adaptive} and \emph{hardware accelerated} formation of acoustic images: the first three reconstruct them from acoustic echoes and the last synthesizes them through acoustic simulation.

>>>>

We present four journal published papers concerned with \emph{adaptive} and \emph{hardware accelerated} formation of acoustic images: the first three reconstruct from echoes and the last synthesizes through simulation.

### 2019-06-30 ThesisJo/frontmatter.tex
2019-06-29

This journey seems to have started a different life ago. Along the way more appreciation has piled up in the depths of my heart than I believed possible. I can only hope to give a little back by extending my sincerest gratitude to

@@

\emph{the Department of Informatics, IFE}, for initially granting me this opportunity and later extending it;

\emph{the Norwegian Defence Research Institute, FFI}, for providing data to study and being an amazing workplace;

@@

\emph{my family}, for all your support, love and presence---through good and bad;

(\emph{myself}, I could not have done it without you;)

@@

\textit{Cognition:}\\The mental action or process or acquiring knowledge and understanding through thought, experience, and the senses.

>>>>

This journey seems to have started a different life ago. Along the way more appreciation has piled up in the depths of my heart than I believed possible. I can only hope to give a little back by extending my sincerest gratitude to the following:

@@

\emph{The Department of Informatics, IFE}, for initially granting me this opportunity and later extending it;

\emph{The Norwegian Defence Research Institute, FFI}, for providing data to study and being an amazing workplace;

@@

\emph{My family}, for all your support, love and presence---through good and bad;

\emph{Myself}, I could not have done it without you ;)

@@

\textit{Cognition:}\\The mental action or process of acquiring knowledge and understanding through thought, experience and the senses.
